% resume.tex
% vim:set ft=tex spell:

\documentclass[10.5pt]{article}
\topmargin=0.0in %length of margin at the top of the page (1 inch added by default)
\oddsidemargin=0.0in %length of margin on sides for odd pages
\evensidemargin=0in %length of margin on sides for even pages
\textwidth=6.0in %How wide you want your text to be
\marginparwidth=0.4in
\headheight=0pt %1in margins at top and bottom (1 inch is added to this value by default)
\headsep=0pt %Increase to increase white space in between headers and the top of the page
\textheight=5.0in %How tall the text body is allowed to be on each page
\usepackage[letterpaper,margin=0.2in]{geometry}
\usepackage{verbatim}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{pslatex}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}
\renewcommand{\labelitemi}{{\tiny$\bullet$}}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}


% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{V VIDYA}}

2, Jai Apartments, IP Extension, Patparganj, New Delhi 110092, India
\\
Tel: +91-9899761567\ \ \textbullet
\ \ Email: vidya.vnv@gmail.com
\\http://www.nsitonline.in/people/vidya.v
\\http://www.github.com/vidyavnv
\end{center}
\vspace{-0.2em}
\hrule
\vspace{-0.2em}
%\begin{center}
%Graduated from 
%\end{center}
\vspace{-0.5em}
\normalsize
\subsection*{EDUCATION}
\vspace{-3pt}
\headerrow
		{\textbf{University of Delhi}, Netaji Subhas Institute of Technology}
                {Delhi, India}
\headerrow
               {B.E. (Information Technology), 70.11\%}
               {2014}
\\[0.07in]
\headerrow
		{\textbf{CBSE}, Bal Bhavan Public School}
                {Delhi, India}
\headerrow
{12th standard,    Percentage: 90.4\%}
{2009}
\headerrow
{10th standard,    Percentage: 94.2\% }
{2007}	
	
	
\subsection*{EXPERIENCE}
\vspace{-3pt}
\headerrow
		{\textbf{American Express India Pvt. Ltd.}}
		{Gurgaon, India}
	\headerrow
		{\emph{Software Engineer}}
		{\emph{2014 - Present}}
$\bullet$ Currently working on building an application using Python and Pig which assigns customers, a score, for efficient campaign 
\\\hspace*{2.5mm}management. 
\\[0.06in]
	\headerrow
		{\textbf{InfoAssembly {\it  - Creates and designs data that enables intended data discovery customized to user's needs}}}
		{Delhi, India}
	\headerrow
		{\emph{Software Engineer, Intern}}
		{\emph{2013}}
$\bullet$ Built a {\it {\bf web crawler }} to parse RSS, PDF and XSL links on a set of user defined domains using Scrapy. 
\\
$\bullet$ {\it {\bf Developed an API }} in Python for Socrata(cloud-software company) to scrape data for over 1500 domains.
\\
$\bullet$ Built  {\it {\bf Mongo Service Layer }} to optimize the database interactions with the client using Python and MongoDB. 
\\
$\bullet$ Built a  {\it {\bf Chrome Extension }} with NodeJS and MongoDB to extract data from websites and store it in a  database.
\\[0.06in]
\headerrow
		{\textbf{Buyingiq.com {\it -  Online Shopping Advisor}}}
		{Delhi, India}
	\headerrow
		{\emph{Software Engineer, Intern}}
		{\emph{2013}}
$\bullet$ Built {\it {\bf Recommendation Engine}} through Item based Collaborative Filtering algorithm which takes into account binary 
\\\hspace*{2.5mm}ratings(viewed/not viewed by users), using PHP and PDO API, which had a run time of 13 seconds over a data of 11000 user entries.
\\
$\bullet$ The engine  predicts  top 5 products to present under the feature "People who viewed this item also viewed".
\\
$\bullet$ Used Model based Collaborative Filtering approach after analysing a number of recommendation systems.
\\[0.06in]
	\headerrow
		{\textbf{GENPACT}}
		{Delhi, India}
	\\
	\headerrow
	        {\emph{Software Engineer, Summer Trainee}}
		{\emph{2012}}
$\bullet$ Worked in a team that developed {\it {\bf HelpDesk application}} where cases are generated through different channels.
\\
$\bullet$ Developed the code on the Front end using Java and JSP which serves more than  {\it {\bf  3k users }} in the organization. 

\subsection*{ACADEMIC PROJECTS}
\vspace{-3pt}
{\it {\bf Predict Stock Prices using Tweets, Headlines and Google Analytics}}
\\
$\bullet$ Collected stock prices and headlines from Google Finance and Yahoo Finance using {\it {\bf Python's BeautifulSoup}}.
\\
$\bullet$ Employed a pilot approach of evaluating one company on all three parameters- stocks, tweets and headlines.
\\
$\bullet$ Used Google Analytics to reduce error in prediction and expanding the project to involve various market sectors.
\\[0.06in]
{\it {\bf Sentiment Analysis of Users' Reviews on IMDB Movies}}
\\
$\bullet$ Applied Naive Bayes classifier using NLTK in  {\it {\bf Python}} to classify reviews into positive or negative class with an accuracy of {\it {\bf 74\%}}.
\\
$\bullet$ Developed a feature mechanism in {\it {\bf Python}} which selects top N words to classify the reviews. This increased the accuracy to {\it {\bf 84\%}}.
\\[0.06in]
{\it {\bf Automatic Detection of Anatomical Structures In Heavily Abnormal Retinal Images for the Detection of  Glaucomatous Changes}}
\\
$\bullet$ Developed an algorithm to detect optic disc and macula using MATLAB which has a success rate of {\it{\bf 90\% }}. 
\\
$\bullet$ Worken on applying machine learning techniques to identify the optic disc and optimize the algorithm. 
\\
$\bullet$ Performed a literature survey on optic disc and macula identification on retinal or fundus images.
\\[0.06in]
{\it {\bf E-Commerce Website Design and Development}}
\\
$\bullet$ Designed an E-Commerce Website using PHP and MySQL supporting 200 products and a shopping cart. 
\\
$\bullet$ Built an Entity-Relationship, SRS and UML model for an E-Commerce Website and for a Social Networking Website. 
\\[0.06in]
{\it {\bf Other Projects}}
\\
$\bullet$ Predicted the area burnt by the forest fires using Linear Regression with 85\% accuracy. All implementation was done using WEKA.
\\
$\bullet$ Developed  Payroll Management System in C++ as a part of high school project.

\subsection*{SKILLS}
\vspace{-3pt}
\hyphenpenalty=1000

	{\it {\bf Programming: }}C, \CPP, Python, NodeJs, Javascript, PHP, HTML, Matlab  
         \hspace*{20.5mm}{\it {\bf Operating Systems: }}UNIX, WINDOWS    
	\\{\it {\bf Tools: }}WEKA, XCode, Git, LAMP, Eclipse
          \hspace*{62mm}{\it {\bf Databases: }}MySQL, MongoDB, Oracle 9i  
         \\{\it {\bf Languages:}}English, Hindi, German  
   

\subsection*{LEADERSHIP SKILLS }
\vspace{-3pt}
{\emph{President}}, The NSIT Quiz Club
\\
$\bullet$ Promoted to President in Spring 2013; led a team of  {\it {\bf 30}} people to ensure effective running of NSIT's largest ever quizzing festival, with participation increasing to  {\it {\bf three times}} previous years'. 
\\
$\bullet$ Raised  {\it {\bf 75\% }}of sponsorship within 2 weeks. 
\\
$\bullet$ Handled the accounts for the NSIT Quiz Fest 2013 and NSIT Quiz Fest 2012 as the Treasurer.
\\
\\
{\emph{Co-Founder, Webmaster}}, ACM NSIT Student Chapter
\\
$\bullet$ {\it {\bf Co-founded the society}} in order to encourage undergraduate research among students in various areas of computer science through
\\\hspace*{2.5mm}research talks and competitions.
\\
$\bullet$ Spearheaded the design team to complete the extensively detailed website(http://nsit.acm.org/) within a month(2 months
\\\hspace*{2.5mm}before target), using WordPress, PHP, HTML and CSS. It gained 11000 hits within a span of 5 months.
\\
\\
{\emph{Lead Developer}},	NSITOnline - Official NSIT Portal
\\
$\bullet$ Developed official NSIT forum http://forum.nsitonline.in/ using phpBB, Joomla and Facebook API for resolving student queries regarding
 \\\hspace*{2.5mm}  admission and placements.
\\
$\bullet$ Developed the website http://www.nsitonline.in/ which serves as a portal for the Training and Placement team and is a consolidated source for 
 \\\hspace*{2.5mm} information and resources for the students. 
\\
\\
{\emph{Team Captain}}, Basketball
\\
$\bullet$ Excellent time management skills. Balanced a 40+ hour practice, training, competition, and travel schedule, in addition to academics.
\\
$\bullet$ Effectively managed communications between 15 team members, served as a liaison between the team and coaching staff and effectively resolved 
\\\hspace*{2.5mm} intra-team conflicts.



\subsection*{ACHIEVEMENTS}
\vspace{-3pt}
$\bullet$ Graduated in Introduction to Artificial Intelligence conducted by Stanford University. 
\\
$\bullet$ In top 0.5\% in All India Engineering Entrance Examination (AIEEE) out of 11 lakh students nationally.
\\
$\bullet$ In top 2\% in Indian Institute of Technology Joint Entrance Exam (IIT-JEE) out of 4 lakh students nationally.
\\
$\bullet$ Top 3 scorers in 10th and 12th board CBSE Examination in School.


\subsection*{RELEVANT COURSEWORK}
\vspace{-3pt}
{Data Structures, Algorithms, Theory of Computation, Database Systems, Operating Systems, Software Engineering,Computer Networks,
\\  Artificial Intelligence, Machine Learning.}
\end{document}
